---
title: "HarpethTMDL"
author: "RJ"
date: "`r Sys.Date()`"
output: github_document
---

```{r, Intro, eval=TRUE}

WASP.version<-8



```

# Introduction

**Harpeth TMDL** --  Water Quality Analysis Simulation Program (WASP version `r WASP.version`)

Exploration of water quality data using the calibrated WASP models provided to TDEC and others by the EPA Region 4


```{r, Setup, warning=FALSE, include=TRUE, echo=TRUE, error=FALSE, message=FALSE, collapse=TRUE}
#Load in required packages

library(tidyverse)
library(osmdata) 
library(ggmap)
library(dataRetrieval)
library(XML)
library(DT)
library(dbplyr)
library(widgetframe)
library(rgdal)
library(leaflet)
library(plotly)
library(formattable)
library(htmltools)
library(leaflet)
library(sf)
library(kableExtra)
library(knitr)
library(wql)

time = lubridate::with_tz(Sys.time(), "CST6CDT")

```


This file was last updated on `r time`


```{r, Import Data, warning=FALSE, include=TRUE, echo=TRUE, error=FALSE, message=FALSE, collapse=TRUE, tidy=TRUE}

#Import Data

library(readxl)
Grab <- read_excel("GrabSamples.xlsx", 
    col_types = c("skip", "text", "text", 
        "skip", "skip", "date", "text", "numeric", 
        "text"))

head(Grab,15)







```


`Grab` data table contains grab sample results collected from `r length(unique(Grab$Station_ID))` locations throughout the Harpeth River watershed





